Forecasting U.S. Presidential Election Outcomes: A Poll-Based Predictive Model Using YouGov Data

### 2024-11-03 paper/paper.qmd
Some small fix and add some contents

library(tidyverse)
library(rstanarm)
library(modelsummary)
library(kableExtra)

@@

analysis_data <- read_csv(here::here("data/02-analysis_data/analysis_data.csv"))

>>>>

library(tidyverse)
library(rstanarm)
library(modelsummary)
library(kableExtra)
library(arrow)

@@

analysis_data <- read_parquet(here::here("data/02-analysis_data/analysis_data.parquet"))
